hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-02-26 inst/manuscript/paper_pdf/paper.Rmd
add additional sections at end (Conflict of Interest, funding, etc.)
Switch to APA reference style, add APA.csl

---
title: ""
output: pdf_document
header-includes:
   - \usepackage{lineno}
   - \linenumbers
bibliography: ms_refs.bib
---

@@

Morgan Sparks^1^, Eli Felts^2^, Allison Swartz^3^, Bryan Maitland^1^

@@

@@

>>>>

---
title: ""
output: pdf_document
header-includes:
   - \usepackage{lineno}
   - \linenumbers
bibliography: ms_refs.bib
csl: apa.csl
---

@@

Morgan Sparks^1,4^, Eli Felts^2^, Allison Swartz^3^, Bryan Maitland^1^

@@

^4^Corresponding Author: Morgan M. Sparks, Morgan.Sparks\@USDA.gov

@@

# Acknowledgements

We thank Laura Koller for her help designing the **hatchR** logo. Dan Isaak provided useful discussion about model development and temperature data sets.

The views expressed in this manuscript are those of the authors and do not necessarily represent the views or policies of USFS or USFWS. Any mention of trade names, products, or services does not imply an endorsement by the U.S. government, USFS, or USFWS. USFS and USFWS do not endorse any commercial products, services or enterprises.

# Conflicts of Interest

The authors declare no known conflicts of interest.

# Data Availability

**hathcR** is fully open source and reproducible. Source code and data can be found at <https://github.com/bmait101/hatchR/>. The latest version will be archived upon acceptance of the manuscript.

# Ethics Statement

All data was derived from pre-published sources or created synthetically.

# Funding

The authors declare no funding sources.
